Supplement 2: Stationwise Evaluation

### 2018-10-03 pkg/disttree/inst/draft/supplement/supplement_stationwise.Rnw
added explanation of PIT histograms and residual QQ plots
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2304 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: aabc77b81fc38653de06e4077285ccca60181093

\item \emph{PIT histograms:} Similarly, the out-of-sample probability integral
transform (PIT) in the single-split setting is amployed as an alternative
goodness-of-fit visualization.

@@

>>>>

\item \emph{PIT histograms:} Similarly, the out-of-sample probability integral
transform (PIT) in the single-split setting is employed as an alternative
goodness-of-fit visualization.

@@

The Resiudal QQ plots and the PIT histograms visualize the same values,
however, on different scales. For each observation $y$ of the test sample 
the corresponding PIT value is calculated by applying the probability function 
$F(y; \hat{\mu}, \hat{\sigma})$
with the estimated distribution parameters plugged in. The resulting values
can either be plotted in a histogram (PIT histogram) or be plotted against
the corresponding quantiles of a standard normal distribution (residual QQ plot)
for a continuous variable $Y$. To account for the point mass at 0, for each 
observation equal to 0 the corresponding PIT value is multiplied with a randomized
value following a uniform distribution on \[0,1\]. In that way these values
are apportioned on those bins of the histogram that would not contain any
values because no observation is beneath 0.
